Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-04 paper/main.tex
working on methods; backing up current progress

@@

@@

>>>>

We enrolled a total of 491 Dartmouth undergraduate students across 11
experimental conditions. The conditions included two primary controls (feature
rich, reduced), two secondary controls (reduced (early), reduced (late)), six
order manipulation conditions (category, size, length, first letter, color, and
locaiton), and a final adaptive condition. Each of these conditions are
described in the \textit{Experimental design} subsection below.

Participants received course credit for enrolling in our study. We asked each
participant to fill out a demographic survey that included information about
their self-reported age, gender, ethnicity, race, education, vision, reading
impairments, medications or recent injuries, coffee consumption on the day of
testing, and level of alertness at the time of testing. All components of the
demographics survey were optional. One participant elected not to fill out any
part of the demographic survey, and all other participants report some or all
of their requested demographic information.

We aimed to run (to completion) at least 60 participants in each of the two
primary control conditions and in the adaptive condition. In all other
conditions we set a target enrollment of at least 30 participants. Because our
data collection efforts were coordinated 12 researchers and multiple testing
rooms and computers, it was not feasible for individual experimenters to know
how many participants had been run in each experimental condition until the
relevant databases were synchronized at the end of each working day. We also
over-enrolled participants for each condition to help ensure that we met our
minimum enrollment targets even if some participants dropped out of the study
prematurely or did not show up for their testing session. This led us to exceed
our target enrollments for several conditions.

Participants were assigned to experimental conditions based loosely on their
date of participation. (This aspect of our procedure helped us to more easily
synchronize the experiment databases across multiple testing computers.)
A complete report... %STOPPED HERE

@@

Our experiment is a variant of the classic free recall paradigm that we term
\textit{feature-rich free recall}. In feature-rich free recall, participants
study 16 lists, each comprised of 16 words that vary along a number of stimulus
dimensions: semantic category, object size, text color, text location, word
length, and starting letter (Fig.~\ref{fig:exp1}). Each list contains four
words from each of four different semantic categories; all other stimulus
features are randomized. After studying each list, the participant attempts to
recall as many words as they can from that list, in any order they choose.
Because each individual word is associated with several well-defined (and
quantifiable) features, and because each list incorporates a diverse mix of
feature values along each dimension, this allows us to evaluate participants'
memory fingerprints in rich detail.

Our experimental paradigm incorporates the Annyang and Google Cloud Speech API
speech-to-text engines to automatically transcribe participants' verbal recalls
into text. This allows recalls to be transcribed in real time-- a
distinguishing feature of the experiment; in typical verbal recall experiments
the audio data must be parsed manually. (We have run a pilot experiment to
verify that the automatically transcribed recalls are sufficiently close to
human-transcribed recalls to yield reliable data.) This real-time speech
processing component of the paradigm plays an important role in Experiments
3--5.

\subsubsection*{Stimuli}

\subsubsection*{Real-time speech-to-text processing}

\subsubsection*{Order manipulation conditions}

\paragraph{Feature dimensions.}

\paragraph{Constructing feature-sorted lists.}

\subsubsection*{Random conditions}

\subsubsection*{Adaptive conditions}

\paragraph{Online ``fingerprint'' analysis.}

\paragraph{Ordering ``stabilize'' lists by an estimated fingerprint.}

\paragraph{Ordering ``destabilize'' lists by an estimated fingerprint.}

@@

\subsubsection*{Probability of first recall and probability of $n$\textsuperscript{th} recall}

\subsubsection*{Lag conditional response probability}

\subsubsection*{Computing clustering scores and memory fingerprints}

\subsubsection*{Identifying event boundaries}

\subsubsection*{Serial position curves and recall accuracy}

\subsubsection*{Computing low-dimensional embeddings of memory fingerprints}
